### 2014-05-12 ApTranscriptome_TR.Rmd
Updated figures for T_on

# plot
T_on_plot <- ggplot(Ap.high.T_on, aes(x=T_on, fill=colony)) + geom_density(alpha=0.2, position="identity")
T_on_plot + scale_y_continuous(name="Density") +
  scale_x_continuous(name=expression("Temperature"))

# plot predicted
pT_on_plot <- ggplot(Ap.high.T_on, aes(x=pT_on, fill=colony)) + geom_density(alpha=0.2, position="identity")
pT_on_plot + scale_y_continuous(name="Density") +
  scale_x_continuous(name=expression("Temperature"))
```

@@

```{r plot_low_T_on, echo=FALSE, eval=TRUE}
# prep data for plotting
Ap.low.T_on <- rbind(A22.low.T_on, Ar.low.T_on)

# plot
T_on_plot_low <- ggplot(Ap.low.T_on, aes(x=T_on, fill=colony)) + geom_density(alpha=0.2, position="identity")
T_on_plot_low + scale_y_continuous(name="Density") +
  scale_x_continuous(name=expression("Temperature"))

# plot predicted
pT_on_plot_low <- ggplot(Ap.low.T_on, aes(x=pT_on, fill=colony)) + geom_density(alpha=0.2, position="identity")
pT_on_plot_low + scale_y_continuous(name="Density") +
  scale_x_continuous(name=expression("Temperature"))
```

>>>>

# plot
T_on_plot_high <- ggplot(Ap.high.T_on, aes(x = T_on, y = ..density.., colour = colony, group = colony, fill = colony)) +
    geom_histogram(position = "dodge", binwidth = 3) +
    geom_density(adjust = 3, fill = NA, size = 2) + 
    scale_y_continuous(name="Density") +
    scale_x_continuous(name=expression("Temperature"))
print(T_on_plot_high)

# plot predicted
pT_on_plot_high <- ggplot(Ap.high.T_on, aes(x = pT_on, y = ..density.., colour = colony, group = colony, fill = colony)) +
    geom_histogram(position = "dodge", binwidth = 3) +
    geom_density(adjust = 3, fill = NA, size = 2) + 
    scale_y_continuous(name="Density") +
    scale_x_continuous(name=expression("Temperature"))
print(pT_on_plot_high)
```

@@

```{r plot_low_T_on, echo=FALSE, eval=TRUE}
# prep data for plotting
Ap.low.T_on <- rbind(A22.low.T_on, Ar.low.T_on)
# plot
T_on_plot_low <- ggplot(Ap.low.T_on, aes(x = T_on, y = ..density.., colour = colony, group = colony, fill = colony)) +
    geom_histogram(position = "dodge", binwidth = 3) +
    geom_density(adjust = 3, fill = NA, size = 2) + 
    scale_y_continuous(name="Density") +
    scale_x_continuous(name=expression("Temperature"))
print(T_on_plot_low)

# plot
pT_on_plot_low <- ggplot(Ap.low.T_on, aes(x = pT_on, y = ..density.., colour = colony, group = colony, fill = colony)) +
    geom_histogram(position = "dodge", binwidth = 3) +
    geom_density(adjust = 3, fill = NA, size = 2) + 
    scale_y_continuous(name="Density") +
    scale_x_continuous(name=expression("Temperature"))
print(pT_on_plot_low)
```
